---
title: "Plotting dagittyplus models with ggdag"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting dagittyplus models with ggdag}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

`dagittyplus` keeps the exported function names and the `dagitty` S3 class of the
upstream `dagitty` package unchanged. As a result, models you build with
`dagittyplus` are ordinary `dagitty` objects, and the
[`ggdag`](https://r-causal.github.io/ggdag/) package (Barrett), which is built on
top of `dagitty`, can tidy and plot them with `ggplot2` without any conversion.

Build a model the usual way:

```{r}
library(dagittyplus)

g <- dagitty("dag {
  x [exposure]
  y [outcome]
  z -> x
  z -> y
  x -> y
}")

class(g)
```

The object has class `"dagitty"`, so every `ggdag` function accepts it directly.
The examples below are not run here (so that this vignette does not require
`ggdag` to be installed), but they work as written once you
`install.packages("ggdag")`:

```{r, eval = FALSE}
library(ggdag)

# Tidy the model into a tibble of nodes and edges.
tidy_dagitty(g)

# Plot it with ggplot2.
ggdag(g) +
  theme_dag()

# Highlight a minimal sufficient adjustment set for the effect of x on y.
ggdag_adjustment_set(g)
```

Because both packages share the same `dagitty` representation, you can move
freely between `dagittyplus` for analysis and `ggdag` for publication-quality
figures.
